\pagestyle{headings}

\pagenumbering{roman}       % Number the first few pages in roman
\vspace*{1in}
\begin{center}
    {\Huge SPICE:}           \\[1in]
    {\Large User's Guide and Reference}
     \\[0.5in] \large\sl
                  July 2, 2007\\[0.5in]
                  Edition 1.3
          \\[0.5in]
          Michael B. Steer
              \\[2in]
              A manual created to support the development of fREEDA$^{\mathrm TMa}$ (http://www.freeda.org).
\end{center}
\newpage

\noindent Copyright \copyright\ 1993,2007 by  Michael B.
Steer  $<$ m.b.steer@ieee.org $>$
\vfill

\noindent All rights reserved. Published as an on-line electronic book by Michael Steer, 2007. This publication may be reproduced, stored in
a data base or retrieval system or transmitted, in any form or by
any means, electronic, mechanical, photocopying, recording or
otherwise without permission. \vfill
%\accusim\ is a trademark of Mentor Graphics.\\
%\cdsspice\ is a trademark of Cadence Design Systems.\\
%\hpimpulse\ is a trademark of Hewlett Packard.\\
%\hspice\ is a trademark of Meta-Software.\\
%\igspice\ is a trademark of A.B. Associates.\\
%\isspice\ is a trademark of IntuSoft.\\
%\mspice\ is a trademark of EEsof.\\
%\spectre\ is a trademark of Cadence Design Systems.\\
\noindent\spicetwo\ is a trademark of U.C. Berkeley.\\
\spicethree\ is a trademark of U.C. Berkeley.\\
%\spiceplus \ is a trademark of Valid Logic.\\
\notforsspice{\pspice\ probe, parts, device equations and digital files are trademarks of Microsim Corp.\\}
All other trademarks are the properties of their respective owners.

\vfill
\noindent This document was prepared using \LaTeX.\\
Diagrams were prepared using idraw, xfig and gnuplot.
\vfill

{\scriptsize \baselineskip=6pt
\noindent Information contained in this work is believed to be reliable and
obtained from sources that are also believed to be reliable.
However, the author does not guarantee the completeness or
accuracy of any information contained herein and the author shall not be responsible for any errors, omissions, or damages
arising out of use of this information.
This work is published with the understanding that the
author is supplying information but are not attempting to render
engineering or other professional services. If such
services are required, the assistance of an appropriate professional should
be sought.}
\hspace*{\fill}
\tableofcontents
\listoffigures
\listoftables
%\input{symbo}
\clearpage
\vspace*{0.5in}
\noindent{\Large\bf Preface}\\[0.5in]
This book was begun to develop a multi-version of a SPICE manual to guide the development of the multi-physics simulator fREEDA$^TM$, see http://www.freeda.org. The various version os Spice are not fully compatible which presents challenges in trying to make a new simulator compatible with Spice.


The contributions of Paul Franzon to Chapters 2 and 3 are gratefully acknowledged.\\[0.5in]


\parbox{2in}{Michael Steer\newline
North Carolina State University\newline
email: mbs@ncsu.edu}
