%\chapter*{References}\markboth{REFERENCES}{REFERENCES}
\addcontentsline{toc}{chapter}{\numberline {}References}
Descriptions of the basic algorithms of \Spice.
\begin{thebibliography}{999}
\bibitem{mccalla}
McCalla

Descriptions of MOSFET models.

\bibitem{antognetti:massobrio:88}
P. Antognetti and G. Massobrio (editors),
{\it Semiconductor Device Modeling with SPICE}, McGraw-Hill: New York,
1988.

\bibitem{shichman:hodges:68}
H. Shichman and D.~A. Hodges, ``Modeling and simulation of insulated-gate
field-effect transistor switching circuits,''
{\it IEEE Journal of Solid-State Circuits}, Vol. 3, September 1968, Page 285.

\bibitem{meyer:71}
J.~E. Meyer, ``MOS models and circuit simulation,''
{\it RCA Review}, Vol 32., 1971.

\bibitem{ward:dutton:78}
D.~E. Ward and R.~W. Dutton, ``A channel-oriented model for MOS transistors
capacitances,'' {\it IEEE J. Solid-State Circuits}, Vol. 13, 1978.

\bibitem{oh:ward:80}
S.~Y. Oh, D.~E. Ward and R.~W. Dutton,
``Transisent analysis of MOS transistors,''
{\it IEEE Trans. Electron Devices}, Vol. 27, No. 8, 1980.

\bibitem{vladimirescu:liu:80}
A. Vladimirescu and S. Liu, {\it The simulation of MOS transistor integrated
circuits using SPICE2},
University of California, Berkeley,
Memorandum No. M80/7, February 1980.

\bibitem{lee:shur:93}
K. Lee, M. Shur, T. Fjeldly and T. Ytterdal, {\it Semiconductor Device
Modeling for VLSI}, Prentice Hall: Englewood Cliffs, New Jersey, 1993.


\bibitem{sheu:scharfetter:87}
B.~J. Sheu, D.L. Scharfetter, P.-K. Ko, and M.-C. Jeng, ``BSIM:
Berkeley Short-Channel IGFET model for MOS transistors,''
{\it IEEE Journal of Solid-State Circuits}, Vol 22, August 1987, pp. 558-566.

\bibitem{pierret:84}
J.~R. Pierret, `` {\it A MOS Parameter extraction program for the BSIM model},
University of California, Berkeley,
Memorandum No. M84/99, November 1984.


Descriptions of MESFET models.

\bibitem{curtice:80}
W.~R. Curtice, ``A MESFET model for use in the design of GaAs integrated
circuits,'' {\it IEEE Transactions on Microwave Theory and Techniques,}
Vol. 28, pp. 448-456, 1980.

\bibitem{curtice:ettenberg:85} 
{W.R. Curtice and M. Ettenberg, ``A nonlinear GaAs FET model for use in the
design of output circuits for power amplifiers,'' {\it IEEE Trans. on
Microwave Theory and Tech.}, Vol. MTT-33, Dec. 1985, pp. 1383-1393.} 

\bibitem{kacprzak:materka:83} 
{T. Kacprzak and A. Materka,
``Compact dc model of GaAs FET's for large-signal computer calculation,''
{\it IEEE Journal of Solid-State Circuits},
Vol. SC-18, April 1983, pp. 211-213.} 
  
\bibitem{sussman-fort}
S.E. Sussman-Fort,
``On the basic algorithms of SPICE with application to microwave circuit
simulation,'' {\it Presented at Nonlinear CAD and Modeling Workshop},
IEEE International Microwave Symp. 1987

\bibitem{sussman-fort:narasimhan:84} 
{S.E. Sussman-Fort, S. Narasimhan, and K. Mayaram,
``A complete GaAs MESFET computer model for SPICE,''
{\it IEEE Trans. Microwave Theory and Tech.},
Vol. MTT-32, April 1984, pp. 471-473.} 
 
\bibitem{sussman-fort:hantgan:86} 
{S.E. Sussman-Fort, J.C. Hantgan, and F.L. Huang,
``A SPICE model for enhancement- and depletion-mode GaAs FET's,''
{\it IEEE Trans. Microwave Theory Tech.},
Vol. MTT-34, Nov. 1986, pp. 1115-1118.} 

\bibitem{golio:hauser:85} 
{J.M. Golio, J.R. Hauser, and P.A. Blakey,
``A large-signal GaAs MESFET model implemented on SPICE,''
{\it IEEE Circuits and Devices Magazine},
 Sep. 1985, pp. 21-30.} 
 
\bibitem{golio:blakey:85} 
{J.M. Golio, P.A. Blakey, and R.O. Grondin,
``A general CAD tool for large-signal GaAs MESFET circuit design,''
{\it IEEE MTT-S International Microwave Symposium Digest},
 June 1985, pp. 417-420.} 

\bibitem{angelov:zirath}
Angelov:Zirath

\bibitem{golio:hauser:85} 
{J.M. Golio, J.R. Hauser and  P.A. Blakey
``A large-signal GaAs MESFET model implemented on SPICE,''
{\it IEEE Circuits and Devices Magazine},
 Sept. 1985, pp. 21-30.} 

\bibitem{golio:blakey:20} 
{J.M. Golio, P.A. Blakey, and R.O. Grondin,
``A general CAD tool for large-signal GaAs MESFET circuit design,''
{\it IEEE MTT-S Digest},
 417-420,.} 

\bibitem{ladbrooke:88} 
{P.H. Ladbrooke,
``Reverse modelling of GaAs MESFETs and HEMTs,''
{\it GEC Journal of Research},
Vol. 6, 1988, pp. 1-9.} 

\bibitem{statz:87}
H. Statz, P. Newman, I.~.W. Smith, R.~A. Pucel and H.~A. Haus,
``GaAs FET Device and Circuit Simulation in SPICE,''
{\it IEEE Transactions on Electron Devices}, Vol. 34, pp 160--169, 1987.

\bibitem{mccamant:mccormack:90}
A. J. McCamant, G. D. McCormack, and D. H. Smith, ``An improved GaAs MESFET
Model for SPICE,'' {\it IEEE Transactions on Microwave Theory and Techniques},
Vol. 38, pp. 822-824, June 1990.

Descriptions of transformer model.

\bibitem{jiles:atherton:86}
D.~C. Jiles and D.~L. Atherton, ``Theory of ferromagnetic hysteresis,''
{\it Journal of Magnetism and Magnetic Materials}, Vol. 61, 1986. pp. 48

\bibitem{divekar:87}
D. Divekar, ``Comments no `GaAs FET devices and circuit simulation ni
SPICE,' {\it IEEE Trans. on Electron Devices}, Vol. 34, December 1987,
p. 2564.

\bibitem{smith:87}
I.W. Smith, H. Statz, H.A. Haus, and R.A. Pucel,
``On charge nonconservation in FETs,'' 
{\it IEEE Trans. on Electron Devices}, Vol. 34, December 1987, pp.2565-2568.

Miscellaneous


\bibitem{knuth:subtractive}
D.~Knuth, {\it The Art of Computer programming}, Vol. 2.

\bibitem{sze2e}
S. M. Sze, {\it Physics of Semiconductor Devices}, 2nd Edition, John Wiley
and Sons: New York, 1981

\bibitem{szehighspeed}
S. M. Sze, {\it High-Speed Semiconductor Devices}, John Wiley
and Sons: New York, 1990.

\end{thebibliography}
