\element{U}{Universal Element}

The {\tt U} element is a universal element for extending the
number of elements that \justspice\ can handle. The element is
determined by the model type. In some cases model parameters
indicate further refinement.

Since the \justspice\ {\tt U} element is used to specify many
different kinds of physical elements there is no common form for
it.  Each physical element is distinguished by the type of the
model it refers to.  The format and description of each element is
given in the model description as indicated in the following
table. The index is used in this manual to uniquely identify the
various elements.

\vfill \modeltype{} \hspace*{\fill}
\begin{tabular}{|p{0.6in}|p{0.6in}|p{3in}|}
\hline
Model & Index & Description\\
\hline \hline STRUC&STRUC&Geometric coupled, lossy planar
transmission line
      \newline \sspice\ only.\\
\hline U&U311    &Geometric coupled planar transmission line (up
to 5 lines)
      \newline Identifying Model Parameters:
      {\tt LEVEL=3} {\tt EVEL=1} {\tt PVEL=1}
      \newline \hspice\ only.\\
\hline U&U312    &Geometric coaxial cable
      \newline Identifying Model Parameters:
      {\tt LEVEL=3} {\tt EVEL=1} {\tt PVEL=2}
      \newline \hspice\ only.\\
\hline U&32    &General transmission line (up to 5 lines) defined
by precomputed
      parameters.
      \newline Identifying Model Parameters:
      {\tt LEVEL=3} {\tt EVEL=2}
      \newline \hspice\ only.\\
\hline U&U34    &General transmission line (up to 5 lines) defined
by measurements.
      \newline Identifying Model Parameters:
      {\tt LEVEL=3} {\tt EVEL=3}
      \newline \hspice\ only.\\
\hline U&U4    &Digital output element
      \newline Identifying Model Parameter: {\tt LEVEL=4}
      \newline \hspice\ only.\\
\hline U&U5    &Digital input element
      \newline Identifying Model Parameter: {\tt LEVEL=5}
      \newline \hspice\ only.\\
\hline
\end{tabular}

\hspace*{\fill}
\begin{tabular}{|p{0.6in}|p{0.6in}|p{3in}|}
\hline
Model & Index & Description\\
\hline \hline UDLY&UDLY & Delay Line
      \newline \justpspice\ only.\\
\hline UEFF&UEFF & Edge-Triggered Flip-Flop
      \newline \justpspice\ only.\\
\hline UGATE&UGATE& Standard Gate Model Form
      \newline \justpspice\ only.\\
\hline UGFF&UGFF & Gated Flip-Flop
      \newline \justpspice\ only.\\
\hline UIO&UIO  & IO Model
      \newline \justpspice\ only.\\
\hline URC&URC  &Lossy RC transmission line
      \newline \spicethree\ only.\\
\hline USUHD&USUHD& Setup and Hold Checker
      \newline \justpspice\ only.\\
\hline UTGATE&UTGATE& Tri-State Gate
      \newline \justpspice\ only.\\
\hline UWDTH&UWDTH& Pulse-Width Checker
      \newline \justpspice\ only.\\
\hline
\end{tabular}

\note{
\item
One of the problems with \justspice\ is that the first letter of
an element's name is used to determine the type of an element. One
consequence of this is that there can only be 26 elements --- one
for each letter of the alphabet.  \spicetwo The original version
of \justspice\  from which all subsequent versions of \justspice\
have been developed had less than 26 elements and so this was not
a problem. With the addition of new element types several of the
originally unised letters were used and a universal element, the
{\tt U} element, introduced to handle even more.  The {\tt U}
element is used to represent many different type of elements such
as lossy transmission lines and digital devices. All of the {\tt
U} elements refer to models and the model name, and sometimes
model parameters, used to indicate the actual element referred
to.

\item
There is no equivalent element in \FDA.}
